---
title: "Test SeedBox"
author: "Sebastien Lindsay"
date: "2022-07-18"
output: html_document
---
## Data Preview

Load the data

```{r}
testSamples <- read.csv("https://raw.githubusercontent.com/seedboxtech/datasciencetest/master/testSamples.csv")
```

```{r}
transData <- read.csv("https://raw.githubusercontent.com/seedboxtech/datasciencetest/master/transData.csv")
```

Merge CSV files

```{r}
mergedfile <- merge(testSamples,transData,by.x = "sample_id",by.y = "sample_id")
head(mergedfile, 10)
```
## Question 1

What is the approximate probability distribution between the test group and the control group?

###### Find Sample Size

###### Groupby count of single column

```{r}
aggregate(mergedfile$test_group, by=list(mergedfile$test_group), FUN=length)
```
The sample size of the control group is 4050.
The sample size of the test group is 3380.
The total sample size is 7430.

##### Find p and q

```{r}
p=4050/7430
p
q=1-p
q
```

##### Find binomial distribution for 400 cancel requests

```{r}
Control_Group <- 0:400

plot(Control_Group, dbinom(Control_Group, size=400, prob=p),type='h')
```

```{r}
Test_Group <- 0:400

plot(Test_Group, dbinom(Test_Group, size=400, prob=q),type='h')
```

## Question 2

Is a user that must call-in to cancel more likely to generate at least 1 addition REBILL?

###### Make a table of category proportions

```{r}
prop.table(table(mergedfile$transaction_type,(mergedfile$test_group)))*100
```

Yes. Based on the sample, a user that must call-in to cancel have 43,1% chance to generate at least 1 addition REBILL.

## Question 3

Is a user that must call-in to cancel more likely to generate more revenues?

###### Total Revenue by test_group

```{r}
aggregate(x = mergedfile$transaction_amount,                # Specify data column
          by = list(mergedfile$test_group),              # Specify group indicator
          FUN = sum) 
```
Yes. Based on the sample, the Test Group is more likely to generate more revenues compare to the Control Group.

## Question 4

Is a user that must call-in more likely to produce a higher chargeback rate(CHARGEBACKs/REBILLs)?

###### Charge back rate by test_group

```{r}
prop.table(table(mergedfile$transaction_type,(mergedfile$test_group)))*100
```

```{r}
Control_Group = 1.4266487 /  50.5518170
Control_Group
Test_Group = 0.7671602 / 43.1359354
Test_Group
```

No, 0.01778471 < 0.02822151.  Therefore, the test group is less likely to produce a higher chargeback rate compare to the control group.

END

